DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\section{Conclusions}

\tool is able to synthesize dynamic physical plants designed in MATLAB, through transfer-function and state-space representations based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.

Given the current literature in formal synthesis, there is no other MATLAB toolbox for synthesize stable digital systems, while taking into account implementation aspects (fixed-point arithmetic).

As future work, \tool will perform synthesis to generate stable digital controllers and be combined with DSVerifier Toolbox~\cite{issta2017} to verify the stability of the digital controller synthesized, and also, with DSValidator Toolbox~\cite{dsvalidator}, in order to reproduce and validate the stability property.

>>>>

%--------------------------------------
\section{Conclusions}
%--------------------------------------

\tool can synthesize digital controllers for dynamic physical plants 
w.r.t. stability and safety, designed in MATLAB through transfer-function 
and state-space representations using the CEGIS approach.
%
Given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account implementation 
aspects (fixed-point arithmetic). 
%
As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate
 other controller properties (e.g., limit cycle).
